Solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit

### 2016-07-01 paper/paper.tex

\documentclass[12pt]{article}
\bibliographystyle{./style/agufull}
\usepackage[square,comma,authoryear]{natbib}
\usepackage{epsfig}
\usepackage{style/lineno}
\usepackage{amsmath}
%\usepackage{booktabs}
\linenumbers*[1]
\usepackage{subfig}

@@

\begin{table}
\small
%\input{../tables/DeltaBootstraps-case10.txt}
\caption{Results of test on of means of $\rho_{eq}$ shown in the top panel of Figure~\ref{DailyAveragedDstEvents} between days of threshold crossing  near (day = 1 or -1) or on the day of a $D_{st}$ event (day = 0).}
\label{BootstrapDifferenceTable}
\end{table}

@@

\begin{figure}[tp!]
\centering
\includegraphics[scale=0.40]{figures/stormavs-dst.eps}
\\
\rule[1ex]{5cm}{1pt}
\\
\includegraphics[scale=0.40]{figures/stormavs-dd12-GOES6.eps}
\caption{$D_{st}$ events from GOES 6 using hourly medians. Top: Events in the interval 1983-1991; compare to bottom panel Figure~\ref{DailyAveragedDstEvents}. Bottom: Same as Top except for constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours after crossing below $-50$~nT.}
\label{HourlyAveragedDstEvents}
\end{figure}

@@

\clearpage
\begin{figure}[tp!]
  \centering
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBzIMF-case24-t020-tf25-GOES6.eps}
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBzIMF-case24-t025-tf30-GOES6.eps}
  \caption{$\rho_{eq}$ events of Figure~\ref{HourlyAveragedRhoEvents} separated by the average $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
  \label{fig:BzBinned}
\end{figure}

@@

\begin{figure}[tp!]
  \centering
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedkp-case24-t020-tf25-GOES6.eps}
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedkp-case24-t025-tf30-GOES6.eps}
  \caption{Binning $\rho_{eq}$ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
  \label{fig:KpBinned}
\end{figure}

\begin{figure}[tp!]
  \centering
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinneddst-case24-t020-tf25-GOES6.eps}
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinneddst-case24-t025-tf30-GOES6.eps}
  \caption{Binning $\rho_{eq}$ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
  \label{fig:DstBinned}
\end{figure}

>>>>

\documentclass[12pt]{article}
\bibliographystyle{./style/agufull}
\usepackage[square,comma,authoryear]{natbib}
\usepackage{aas_macros}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{style/lineno}
%\usepackage{booktabs}
\linenumbers*[1]
\usepackage{subfig}

@@

\begin{table}
\small
\input{../tables/DeltaBootstraps-case10.txt}
\caption{Results of test on of means of $\rho_{eq}$ shown in the top panel of Figure~\ref{DailyAveragedDstEvents} between days of threshold crossing  near (day = 1 or -1) or on the day of a $D_{st}$ event (day = 0).}
\label{BootstrapDifferenceTable}
\end{table}

@@

\begin{figure}[tp!]
\centering
\includegraphics[scale=0.40]{figures/stormavs-dst-GOES6.eps}
\\
\rule[1ex]{5cm}{1pt}
\\
\includegraphics[scale=0.40]{figures/stormavs-dd12-GOES6.eps}
\caption{$D_{st}$ events from GOES 6 using hourly medians. Top: Events in the interval 1983-1991; compare to bottom panel Figure~\ref{DailyAveragedDstEvents}. Bottom: Same as Top except for constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours after crossing below $-50$~nT.}
\label{HourlyAveragedDstEvents}
\end{figure}

@@

\clearpage
\begin{figure}[tp!]
  \centering
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedB_z-case24-t020-tf25-GOES6.eps}
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedB_z-case24-t025-tf30-GOES6.eps}
  \caption{$\rho_{eq}$ events of Figure~\ref{HourlyAveragedRhoEvents} separated by the average $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
  \label{fig:BzBinned}
\end{figure}

@@

\begin{figure}[tp!]
  \centering
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedKp-case24-t020-tf25-GOES6.eps}
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedKp-case24-t025-tf30-GOES6.eps}
  \caption{Binning $\rho_{eq}$ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
  \label{fig:KpBinned}
\end{figure}

\begin{figure}[tp!]
  \centering
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedDst-case24-t020-tf25-GOES6.eps}
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedDst-case24-t025-tf30-GOES6.eps}
  \caption{Binning $\rho_{eq}$ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
  \label{fig:DstBinned}
\end{figure}
